Childhood exposure to non-persistent endocrine disruptors, glucocorticosteroids, and neurodevelopment: A study based on the parametric g-formula

### 2024-02-13 output/paper/_figures.qmd
Finishing MV v1. Working on tables authors.

```{r}
# Function to align forest plot with table numerical results
forest_plot <- function(obj, r = 4) {
  edcs <- myphd::edcs_information() |>
    dplyr::filter(!chem_id %in% c("dedtp", "dmdtp")) |>
    dplyr::select(chem_id, short_name, class) |>
    dplyr::bind_rows(
      tibble::tibble(
        chem_id = c("Exposure"),
        short_name = c("Exposure"),
        class = c(NULL)
      )
    )

  # From table of numerical results to ggplot object
  tbl_num_res <- obj$numerical_results |>
    tidylog::mutate(
      variable = forcats::fct_reorder2(
        variable, estimate, class
      )
    ) |>
    tidylog::select(-estimate) |>
    dplyr::left_join(
      edcs[, c("chem_id", "short_name")],
      by = c("variable" = "chem_id")
    ) |>
    dplyr::select(-variable) |>
    dplyr::rename(variable = "short_name") |>
    dplyr::relocate(variable) |>
    ggplot2::ggplot(
      ggplot2::aes(
        y = variable,
        shape = outcome
      )
    ) +
    ggplot2::geom_text(
      ggplot2::aes(
        x = 0,
        label = variable
      ),
      hjust = 0,
      fontface = "bold"
    ) +
    ggplot2::geom_text(
      ggplot2::aes(
        x = 1,
        label = val
      ),
      hjust = 0,
      position = ggstance::position_dodgev(height = 0.9)
    ) +
    ggplot2::theme_void() +
    ggplot2::theme(
      strip.background = ggplot2::element_blank(),
      strip.text = ggplot2::element_blank(),
      legend.position = "bottom",
      legend.box = "vertical",
      legend.margin = ggplot2::margin()
    ) +
    ggplot2::coord_cartesian(
      xlim = c(0, 4)
    )

@@

obj3 <- tidy_res_meffects(
  df = marginal_comparisons_3,
  sa_var = NULL,
  outcome = c("hitrtse"),
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)
forest_plot(obj = obj3, r = 5)
```
**Marginal contrasts for the effect of a decrease from the 90th to the 10th percentile of the glucocorticosteroids on {{< acr hitrtse >}} expressed in {{< acr mss >}} (HELIX subcohort; 2013-2016).** 
Circles indicate effect estimates. Solid lines indicate the $95\%$ {{< acr ci >}}.
:::

>>>>

```{r}
# Function to align forest plot with table numerical results
forest_plot <- function(obj, r = 4, is_cortisol = FALSE) {
  edcs <- myphd::edcs_information() |>
    dplyr::filter(!chem_id %in% c("dedtp", "dmdtp")) |>
    dplyr::select(chem_id, short_name, class) |>
    dplyr::bind_rows(
      tibble::tibble(
        chem_id = c("Exposure"),
        short_name = c("Exposure"),
        class = c(NULL)
      )
    )

  # From table of numerical results to ggplot object
  tbl_num_res <- obj$numerical_results
  if (is_cortisol == FALSE) {
    tbl_num_res <- tbl_num_res |>
    dplyr::left_join(
      edcs[, c("chem_id", "short_name")],
      by = c("variable" = "chem_id")
    ) |>
    dplyr::select(-variable) |>
    dplyr::rename(variable = "short_name") |>
    dplyr::relocate(variable)
  }
  tbl_num_res <- tbl_num_res |>
    tidylog::mutate(
      variable = forcats::fct_reorder2(
        variable, estimate, class
      )
    ) |>
    tidylog::select(-estimate) |>
    ggplot2::ggplot(
      ggplot2::aes(
        y = variable,
        shape = outcome
      )
    ) +
    ggplot2::geom_text(
      ggplot2::aes(
        x = 0,
        label = variable
      ),
      hjust = 0,
      fontface = "bold"
    ) +
    ggplot2::geom_text(
      ggplot2::aes(
        x = 1,
        label = val
      ),
      hjust = 0,
      position = ggstance::position_dodgev(height = 0.9)
    ) +
    ggplot2::theme_void() +
    ggplot2::theme(
      strip.background = ggplot2::element_blank(),
      strip.text = ggplot2::element_blank(),
      legend.position = "bottom",
      legend.box = "vertical",
      legend.margin = ggplot2::margin()
    ) +
    ggplot2::coord_cartesian(
      xlim = c(0, 4)
    )

@@

obj3 <- tidy_res_meffects(
  df = marginal_comparisons_3,
  sa_var = NULL,
  outcome = c("hitrtse"),
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)
forest_plot(obj = obj3, r = 5, is_cortisol = TRUE)
```
**Marginal contrasts for the effect of a decrease from the 90th to the 10th percentile of the glucocorticosteroids on {{< acr hitrtse >}} expressed in {{< acr mss >}} (HELIX subcohort; 2013-2016).** 
Circles indicate effect estimates. Solid lines indicate the $95\%$ {{< acr ci >}}.
:::

### 2024-02-13 output/paper/authors.qmd
Switching to new syntax acr. Adding comments from MV v1.
Finishing MV v1. Working on tables authors.

link-citations: true
linkcolor: blue
---

>>>>

link-citations: true
linkcolor: blue

editor_options:
  chunk_output_type: console
---

```{r}
authors <- yaml::read_yaml("../../docs/authors.yml")

proc_one <- function(df, idx) {
  tmp <- df$authors[[idx]]

  affiliations <- unname(unlist(tmp$affiliations))
  full_names <- tibble::tibble(unlist(df$affiliations))
  stringr::str_replace_all()

  ret <- tibble::tribble(
    ~name, ~affiliations, ~role,
    tmp$name, paste0(unname(unlist(tmp$affiliations)), collapse = "; "), paste0(tmp$role, collapse = "; ")
  )
}
```
